A User-Extensible and Adaptable Parser Architecture

### 2008-09-26 doc/sgai-2008-elsevier.tex
Changes needed to make the paper look right.

% $Id$
\documentclass[preprint,draft,numbers]{elsarticle}

@@

% Extra footnote functionality, including references to earlier footnotes.
\usepackage[bottom]{footmisc}

@@

\begin{keyword}
    Parsing
\end{keyword}

@@

The architecture described herein was developed as part of a larger project
to improve anti-spam defences by analysing the performance of the set of
filters currently in use, optimising the order and membership of the set
based on that analysis, and developing supplemental filters where
deficiencies are identified.  Most anti-spam techniques are content-based
(e.g.~\cite{a-plan-for-spam, word-stemming, relaxed-online-svms}) and
require the mail to be accepted before determining if it is spam, but
rejecting mail during the delivery attempt is preferable: senders of
non-spam mail that is mistakenly rejected will receive an immediate
non-delivery notice; resource usage is reduced on the accepting mail server
(allowing more intensive content-based techniques to be used on the mail
that is accepted); users have less spam mail to wade through.  Improving
the performance of anti-spam techniques that are applied when mail is being
transferred via \SMTP{}\footnotemark{} is the goal of this project, by
providing a platform for reasoning about anti-spam filters.  The approach
chosen to measure performance is to analyse the log files produced by the
\SMTP{} server in use, Postfix~\cite{postfix}, rather than modifying it to
generate statistics: this approach improves the chances of other sites
testing and using the software.  The need arose for a parser capable of
dealing with the great number and variety of log lines produced by Postfix:
the parser must be designed so that adding support for parsing new inputs
is a simple task, because the log lines to be parsed will change over time.
The variety in log lines occurs for several reasons:\footnotetext{Simple
Mail Transfer Protocol transfers mail across the Internet from the sender
to one or more recipients.  It is a simple, human readable, plain text
protocol, making it quite easy to test and debug problems with it.  The
original protocol definition is RFC~821~\cite{RFC821}, updated in
RFC~2821~\cite{RFC2821}.}

@@

    \item External resources utilised by Postfix (e.g.\ \DNSBL{} or policy
        servers~\cite{policy-servers}) can change their messages without
        warning.

@@

    \item [Closer to Natural Language Processing than using a fixed
        grammar:] \hfill{}In contrast \newline{} to traditional parsers
        such as those used when compiling a programming language, this
        architecture does not require a fixed grammar specification that
        inputs must adhere to.  The architecture is capable of dealing with
        interleaved inputs, out of order inputs, and ambiguous inputs where
        heuristics must be applied --- all have arisen and been
        successfully accommodated in the Postfix log parser.

@@

Parsing efficiency is an obvious concern when the Postfix log parser
routinely needs to parse large log files.  The mail server which generated
the log files used in testing the Postfix log parser accepts approximately
10,000 mails for 700 users per day; median log file size is 50 MB,
containing 285,000 log lines --- large scale mail servers would have much
larger log files.  When generating the timing data used in this section,
\numberOFlogFILES{} log files (totaling 10.08 GB, \numberOFlogLINEShuman{}
log lines) were each parsed 10 times and the parsing times averaged.
Saving results to the database was disabled for the test runs, because the
tests are aimed at measuring the speed of the Postfix log parser rather
than the speed of the database.  The computer used for test runs is a Dell
Optiplex 745 described in \tableref{Computer used to generate statistics},
dedicated to the task of gathering statistics from test runs.  Parsing all
\numberOFlogFILES{} log files in one run took
\input{build/include-timing-run-duration}, mean throughput is
\input{build/include-timing-run-throughput}; median throughput when parsing
files separately was \input{build/include-median-throughput-MB}
(\input{build/include-median-throughput-log-lines}) parsed per minute.

>>>>

% $Id$
\documentclass[preprint,draft,numbers,1p]{elsarticle}

@@

% Extra footnote functionality, including references to earlier footnotes.
%\usepackage[bottom]{footmisc}

@@

\begin{keyword}
    Parsing \sep{} Postfix \sep{} Anti-Spam \sep{} log files
\end{keyword}

@@

The architecture described herein was developed as part of a larger project
to improve anti-spam defences by analysing the performance of the set of
filters currently in use, optimising the order and membership of the set
based on that analysis, and developing supplemental filters where
deficiencies are identified.  Most anti-spam techniques are content-based
(e.g.~\cite{a-plan-for-spam,word-stemming,relaxed-online-svms}) and
require the mail to be accepted before determining if it is spam, but
rejecting mail during the delivery attempt is preferable: senders of
non-spam mail that is mistakenly rejected will receive an immediate
non-delivery notice; resource usage is reduced on the accepting mail server
(allowing more intensive content-based techniques to be used on the mail
that is accepted); users have less spam mail to wade through.  Improving
the performance of anti-spam techniques that are applied when mail is being
transferred via \SMTP{}\footnotemark{} is the goal of this project, by
providing a platform for reasoning about anti-spam filters.  The approach
chosen to measure performance is to analyse the log files produced by the
\SMTP{} server in use, Postfix~\cite{postfix}, rather than modifying it to
generate statistics: this approach improves the chances of other sites
testing and using the software.  The need arose for a parser capable of
dealing with the great number and variety of log lines produced by Postfix:
the parser must be designed so that adding support for parsing new inputs
is a simple task, because the log lines to be parsed will change over time.
The variety in log lines occurs for several reasons:\footnotetext{Simple
Mail Transfer Protocol transfers mail across the Internet from the sender
to one or more recipients.  It is a simple, human readable, plain text
protocol, making it quite easy to test and debug problems with it.  The
original protocol definition is RFC~821~\cite{RFC821}, updated in
RFC~2821~\cite{RFC2821}.}

@@

    \item External resources Postfix is configured to use (e.g.\ \DNSBL{}
        or policy servers~\cite{policy-servers}) can change their messages
        without warning.

@@

    \item [Closer to Natural Language Processing than using a fixed
        grammar:] \empty{}~\newline{} In contrast to traditional parsers
        such as those used when compiling a programming language, this
        architecture does not require a fixed grammar specification that
        inputs must adhere to.  The architecture is capable of dealing with
        interleaved inputs, out of order inputs, and ambiguous inputs where
        heuristics must be applied --- all have arisen and been
        successfully accommodated in the Postfix log parser.

@@

Parsing efficiency is an obvious concern when the Postfix log parser
routinely needs to parse large log files.  The mail server which generated
the log files used in testing the Postfix log parser accepts approximately
10,000 mails for 700 users per day; median log file size is 50 MB,
containing 285,000 log lines --- large scale mail servers would have much
larger log files.  When generating the timing data used in this section,
\numberOFlogFILES{} log files (totaling 10.08 GB, \numberOFlogLINEShuman{}
log lines) were each parsed 10 times and the parsing times averaged.
Saving results to the database was disabled for the test runs, because the
tests are aimed at measuring the speed of the Postfix log parser rather
than the speed of the database.  The computer used for test runs is a Dell
Optiplex 745 described in \tableref{Computer used to generate statistics},
dedicated to the task of gathering statistics from test runs.  Parsing all
\numberOFlogFILES{} log files in one run took
\input{build/include-timing-run-duration}, mean throughput
\input{build/include-timing-run-throughput}; median throughput when parsing
files separately was \input{build/include-median-throughput-MB}
(\input{build/include-median-throughput-log-lines}) parsed per minute.
